---
title: "R Programming homework 2 Wilson Chau"
output: html_document
date: "2022-07-22"
---
# 1. Use the summary function to gain an overview of the data set.
#Then display the mean and median for at least two attributes.

#check your working directory
```{r getwd()} 
```


```{r}
#import your Rdataset.csv into R studio

homework <- read.csv(file = "CATestscores.csv", header = TRUE, sep = ",")

summary(homework)

mean(homework$english)
median(homework$english)

mean(homework$math)
median(homework$math)

```
#2. Create a new data frame with a subset of the columns and rows.
#Make sure to rename it.


```{r } 
df.CA <- data.frame(homework[sample(1:nrow(homework), 10), c(11:12)])
names(df.CA) <- c("expenditure", "income")
row.names(df.CA) <- 1:10
df.CA
```
#3. Create new column names for the new data frame.
```{r } 
df.CA <- setNames(df.CA, c("Spending Money", "Income"))
df.CA
```

#4. Use the summary function to create an overview of your new data frame. 
#The print the mean and median for the same two attributes. Please compare.

```{r } 
summary(df.CA)
```
#Mean and Median of Spending Money
```{r } 
mean(df.CA$`Spending Money`)
median(df.CA$`Spending Money`)
```
```{r } 
mean(df.CA$Income)
median(df.CA$Income)
```


#5. For at least 3 values in a column please rename so that every value in that 
#column is renamed.For example, suppose I have 20 values of the letter “e” in one column. Rename those values so
#that all 20 would show as “excellent”.

```{r } 
homework <- cbind(homework, school = factor(NA, levels = c("a", "b", "c")))
```

#6 Display enough rows to see examples of all of steps 1-5 above I showed <NA> for School
```{r } 
head(homework, 20)
```